---
title: "CS329e Data Visualization R Project 1"
author: "Nathan Waters, Lerone Williams"
due date: "Wednesday, February 04, 2015"
output: html_document
---

In this R Markdown document we will display and document each step of CS329e R Project 1.

Project Requirements <http://www.cs.utexas.edu/~cannata/dataVis/Projects/R%20Project%201/R%20Project%20Requirements.html>.

In the source folder 01 Data, the R script dataframes.R was created to connect to Dr. Cannata's Orcale database and generate 5 data frames using tables in the Orders Schema. The RCurl package was loaded to allow general HTTP requests and process the results returned by the Web server.

```{r}
source("../01 Data/dataframes.R", echo = TRUE)
```

A second R script dataframes1.R was created to display each data frame that was previously created in the last step. The head() function was used to only return the first parts of each data frame.

```{r}
source("../01 Data/dataframes1.R", echo = TRUE)
```

In order to plot each data frame, the ggplot2 package was loaded and a different geom, short for geometric objects was chosen as follows:
df1 = geom_point(), 
df2 = geom_path(), 
df3 = geom_density2d(),
df4 = geom_dotplot()

```{r}
source("../02 Visualizations/ggplot.R", echo = TRUE)
```

Finally, using the df5 data frame created from the entire data set, the following three plots were produced.

```{r}
source("../02 Visualizations/ggplot1.R", echo = TRUE)
```








